---
title: "Homework 6"
author: Yike Zhao
output: github_document
---

This is my solution to HW6.

```{r}
library(tidyverse)
library(modelr)
library(dplyr)
```

## Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


## Problem 2

```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = as.factor(case_when(
      babysex == 1 ~ "male",
      babysex == 2 ~ "female")
    )
  )
```

For my model, I'd like to asses the relationship between mother's BMI, age at delivery, weights gained during pregnancy and child birth weight. It's reasonable to think that mother's physical condition during pregnancy and delivery would have certain influence on the child.

```{r}
model_1 = lm(bwt ~ momage + ppbmi + wtgain, data=baby_df)

baby_df %>% 
  modelr::add_residuals(model_1) %>% 
  modelr::add_predictions(model_1) %>% 
  ggplot(aes(x=pred, y=resid)) + 
  geom_point()
```

Fit the two other model.

```{r}
model_2 = lm(bwt ~ blength + gaweeks + wtgain, data=baby_df)
model_3 = lm(bwt ~ bhead*blength*babysex, data=baby_df)
```

Cross validation.

```{r}
cv_df =
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    model_1 = map(train, ~lm(bwt ~ momage + ppbmi + wtgain, data = .x)),
    model_2 = map(train, ~lm(bwt ~ blength + gaweeks + wtgain, data = .x)),
    model_3 = map(train, ~lm(bwt ~ bhead*blength*babysex, data = .x))
    ) %>% 
  mutate(
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_model_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y))
    )
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

Through cross validation, we can see that the model 3 with the interactions of head circumference, length, sex has the best prediction accuracy, while the model 1 I constructed has the least accuracy among the three models.



## Problem 3

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Bootstrap r-squared

```{r}
r_df = weather_df %>% 
  modelr::bootstrap(n=5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)
  ) %>% 
  unnest(results) %>% 
  select(r.squared)
```

Plot distribution of r-squared and calculate 95% CI.

```{r}
r_df %>%  
  ggplot(aes(x = r.squared)) + 
  geom_density()
```
```{r}
r_df$r.squared %>% 
  quantile(probs =c(0.025, 0.975)) 
```

The distribution of r-squared has a heavier tail extending to lower values and a shoulder. The 95% CI of r-squared is (0.89, 0.93)

Bootstrap beta

```{r}
beta_df = weather_df %>%
  modelr::bootstrap(n=5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  unnest(results) %>% 
  select(.id, term, estimate) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>% 
  janitor::clean_names() %>% 
  mutate(
    log_beta0beta1 = log(intercept*tmin)
  ) 
```

Plot distribution of r-squared and calculate 95% CI.

```{r}
beta_df %>%  
  ggplot(aes(x = log_beta0beta1)) + 
  geom_density()
```
```{r}
beta_df$log_beta0beta1 %>% 
  quantile(probs =c(0.025, 0.975)) 
```

The distribution of log(beta0 * beta1) has a heavier tail extending to lower values. The 95% CI of log(beta0 * beta1) is (1.97, 2.06)
